---
title: "Lab9"
author: "Yi Wang"
date: "11/14/2018"
output: html_document
---

#1. Submit your solution for the Problem 1 from Activity 9.

```{r}
library(microbenchmark)
odd_count = function(x) {
  odd_num = 0
  for (i in 1:length(x)) {
    if (x[i] %% 2 == 1) 
      odd_num = odd_num + 1
    }
  return(odd_num)
}

odd_count1 = function(x) {
  odd_num = sum(x %% 2 == 1)
  return(odd_num)
}

x = c(1: 100)
microbenchmark(odd_count(x), odd_count1(x))
odd_count1(x)
odd_count(x)
```

#2. Modify the sorting function (sort_vec) from “Assignment 8” (problem 3) so that it should take an additional argument ascending which causes sorting in increasing order when ‘ascending = TRUE’. In other words,
• sort_vect(c(3, 1, 2), ascending = TRUE) = (1, 2, 3)
• sort_vect(c(3, 1, 2), ascending = FALSE) = (3, 2, 1)

```{r}
sort_vect = function(x, ascending) {
  if (length(x) < 2) return (x)
  if (ascending == T){
    for(last in length(x):2) {
      for(first in 1:(last - 1)) {
        if(x[first] > x[first + 1]) {
          temp = x[first]
          x[first] = x[first + 1]
          x[first + 1] = temp
        }
      }
    }
  }
  if (ascending == F){
    for(last in 1:(length(x)-1)) {
      for(first in 1:(length(x)-last)) {
        if(x[first] < x[first + 1]) {
          temp = x[first]
          x[first] = x[first + 1]
          x[first + 1] = temp
        }
      }
    }
  }
  return(x)
}

sort_vect(c(3, 1, 2), ascending = TRUE)
sort_vect(c(3, 1, 2), ascending = FALSE)
```

#3. Consider a simple random walk with starting point 0 and a step -1 or 1. Below is the code with dynamically allocated memory. Write your code with preallocated memory and compare time for both versions using system.time() function (use N = 1000, 10000 and 1000000).
```{r}
N = 1000
data_series = 0
system.time({for (i in 2:N){
  data_series[i] = data_series[i-1] + sample(c(-1, 1), 1)
  }
  })

system.time({
   data_series =  vector(length = N)
    for (i in 2:N){
        data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) }
})
```

```{r}
N = 10000
data_series = 0
system.time({for (i in 2:N){
  data_series[i] = data_series[i-1] + sample(c(-1, 1), 1)
  }
  })

system.time({
   data_series =  vector(length = N)
    for (i in 2:N){
        data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) }
})
```

```{r}
N = 100000
data_series = 0
system.time({for (i in 2:N){
  data_series[i] = data_series[i-1] + sample(c(-1, 1), 1)
  }
  })


system.time({
   data_series =  vector(length = N)
    for (i in 2:N){
        data_series[i] = data_series[i-1] + sample(c(-1, 1), 1) }
})
```

